Gaussian mean estimation in simulated data sets

### 2019-12-20 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

```{r load-pkgs, message=FALSE, warning=FALSE}
library(smashr)
library(ggplot2)
library(cowplot)
source("../code/signals.R")
source("../code/gaussmeanest.functions.R")
```

@@

```{r plot-1-extract-data}
pdat <- get.results.homosked(res,"sp.3.v1")
```

@@

```{r plot-1-create, fig.height=4, fig.width=5}
pdat <-
  transform(pdat,
            method = factor(method,
                            names(sort(tapply(pdat$mise,pdat$method,mean),
                                       decreasing = TRUE))))
p <- ggplot(pdat,aes(x = method,y = mise,fill = method.type)) +
     geom_violin(fill = "skyblue",color = "skyblue") +
     geom_boxplot(width = 0.15,outlier.shape = NA) +
     scale_y_continuous(breaks = seq(6,16,2)) +
     scale_fill_manual(values = c("darkorange","dodgerblue","gold"),
                       guide = FALSE) +
     coord_flip() +
     labs(x = "",y = "MISE") +
     theme(axis.line = element_blank(),
           axis.ticks.y = element_blank())
print(p)
```

From this plot, we see that the three variations of SMASH all
outperformed EbayesThresh and TI thresholding in this setting.

*TO DO: Add bar plots summarizing results from all 7 scenarios and 2
signal-to-noise ratios.*

>>>>

```{r load-pkgs, message=FALSE, warning=FALSE}
library(plyr)
library(smashr)
library(ggplot2)
library(cowplot)
source("../code/signals.R")
source("../code/gaussmeanest.functions.R")
```

@@

```{r homo-extract-data}
pdat <- get.results.homosked(res,"sp.3.v1")
```

@@

```{r create-violin-plot-homo, fig.height=4, fig.width=5}
pdat <-
  transform(pdat,
            method = factor(method,
                            names(sort(tapply(pdat$mise,pdat$method,mean),
                                       decreasing = TRUE))))
p <- ggplot(pdat,aes(x = method,y = mise,fill = method.type)) +
     geom_violin(fill = "skyblue",color = "skyblue") +
     geom_boxplot(width = 0.15,outlier.shape = NA) +
     scale_y_continuous(breaks = seq(6,16,2)) +
     scale_fill_manual(values = c("darkorange","dodgerblue","gold"),
                       guide = FALSE) +
     coord_flip() +
     labs(x = "",y = "MISE") +
     theme(axis.line = element_blank(),
           axis.ticks.y = element_blank())
print(p)
```

From this plot, we see that the three variants of SMASH all
outperformed EbayesThresh and TI thresholding in this setting.

These plots summarize the results for all 7 simulation scenarios and
the two signal-to-noise ratios (1 and 3), including the "Spikes"
scenario shown in greater detail in the violin plot above.

```{r extract-data-for-barplots-homo, fig.height=5, fig.width=8}
create.bar.plots(rbind(
  data.frame(sim = "sp",  snr = 1,get.results.homosked(res,"sp.1.v1")),
  data.frame(sim = "bump",snr = 1,get.results.homosked(res,"bump.1.v1")),
  data.frame(sim = "blkp",snr = 1,get.results.homosked(res,"blk.1.v1")),
  data.frame(sim = "ang", snr = 1,get.results.homosked(res,"ang.1.v1")),
  data.frame(sim = "dop", snr = 1,get.results.homosked(res,"dop.1.v1")),
  data.frame(sim = "blip",snr = 1,get.results.homosked(res,"blip.1.v1")),
  data.frame(sim = "cor", snr = 1,get.results.homosked(res,"cor.1.v1")),
  data.frame(sim = "sp",  snr = 3,get.results.homosked(res,"sp.3.v1")),
  data.frame(sim = "bump",snr = 3,get.results.homosked(res,"bump.3.v1")),
  data.frame(sim = "blkp",snr = 3,get.results.homosked(res,"blk.3.v1")),
  data.frame(sim = "ang", snr = 3,get.results.homosked(res,"ang.3.v1")),
  data.frame(sim = "dop", snr = 3,get.results.homosked(res,"dop.3.v1")),
  data.frame(sim = "blip",snr = 3,get.results.homosked(res,"blip.3.v1")),
  data.frame(sim = "cor", snr = 3,get.results.homosked(res,"cor.3.v1"))))
```
